More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-10-11 2016-Weak-FH-Bisim/WeakBisim.tex
conclusion proof induction

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
\begin{mathpar}
\Bigg(\forall i \in [0\ldots n+1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$ 
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

@@

\item On the other hand, by induction hypothesis we have:
\begin{mathpar}
\bigg(\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}  \wedge

@@

such that\\
$
s_i^6= \left\{
 \begin{array}{ll}
s_i^1 & \mbox{if }i<n_1\\
s_{i-n_1}^3 & \mbox{if }i\geq n_1\\
\end{array}
\right. \, \wedge \,
s_i^8= \left\{
 \begin{array}{ll}
s_i^2 & \mbox{if }i<m_1\\
s_{i-m_1}^5 & \mbox{if }i\geq m_1\\
\end{array}
\right. \\
s\!=\!s^6_0 \wedge s^6_{n_1+n_2}\!=s^7 \wedge s'^7 = s^8_0 \wedge s^8_{m_1+m_2}\!=\!s'\\
~~\\
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^6_i}}
\dotcup\vis{\set{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^8_i}}
}\\
\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\subst{ \biguplus_{i=0}^{n_2}\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^6_i}}
\\
\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\subst{\biguplus_{i=0}^{n_2} \Post^6_i}})^{k\in K}}
$
\end{itemize}

\end{proof}
-----------------------------------------------------

@@

\begin{corollary} The definition of weak bisimulation given in  Definition \ref{def-Weak-bisim} is equivalent to the following weak FH-bisimulation: Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
For any  states
$s\in\mathcal{S}_1$ and
$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
   have:

>>>>

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively). \LUDO{je trouve toujours ca pas tres correct le coup $l=n+m+1$ donc $l'=(n+1)+m+1$ ou $l'=n+(m+1)+1$ mais bon comme on dirait que ma proposition plait pas, on verra a la review}
We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
\begin{mathpar}
\Bigg(\forall i \in [0\ldots n+1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
\end{mathpar}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, \WTUn\ allows us to obtain a similar redution with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$ 
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

@@

\item Concerning the middle reduction, by induction hypothesis there exist a set of transitions in $\mathcal{T}$ such that:
\begin{mathpar}
\bigg(\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}  \wedge

@@

such that\\
$
s_i^6= \left\{
 \begin{array}{ll}
s_i^1 & \mbox{if }i<n_1\\
s_{i-n_1}^3 & \mbox{if }i\geq n_1\\
\end{array}
\right. \, \wedge \,
s_i^8= \left\{
 \begin{array}{ll}
s_i^2 & \mbox{if }i<m_1\\
s_{i-m_1}^5 & \mbox{if }i\geq m_1\\
\end{array}
\right. \\
s\!=\!s^6_0 \wedge s^6_{n_1+n_2}\!=s^7 \wedge s'^7 = s^8_0 \wedge s^8_{m_1+m_2}\!=\!s'\\
~~\\
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^6_i}}
\dotcup\vis{\set{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^8_i}}
}\\
\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\subst{ \biguplus_{i=0}^{n_2}\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^6_i}}
\\
\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\subst{\biguplus_{i=0}^{n_2} \Post^6_i}})^{k\in K}}
$
This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. 
\end{itemize}
\end{proof}
-----------------------------------------------------

@@

\begin{corollary} The definition of weak bisimulation given in  Definition \ref{def-Weak-bisim} is equivalent to the following one:

 Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
For any  states
$s\in\mathcal{S}_1$ and
$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
   have:
